Output Summary

### 2022-01-26 03-post-process/output-plots.Rmd
Update text for pp checks - using Freeman-Tukey now

* **Log-normal**: squared difference of the log-scale observation and log-scale expectation. This applies to all abundance data.
* **Logit-normal**: squared difference of the logit-scale observation and logit-scale expectation. This applies to all survival data, expect pre-spawn survival which used a binomial distribution.
* **Binomial/Multinomial**: chi-squared fit statistic. This applies to all composition data and the pre-spawn survival data.

>>>>

* **Log-normal**: squared difference of the log-scale observation and log-scale expectation. This applies to all abundance data.
* **Logit-normal**: squared difference of the logit-scale observation and logit-scale expectation. This applies to all survival data, except the BON to LGR and the pre-spawn survival which were fitted using binomial distributions.
* **Binomial/Multinomial**: Freeman-Tukey fit statistic, which is similar to the $\chi^2$ statistic but better handles small bin probabilities. This applies to all composition data, the survival from BON to LGR data, and the pre-spawn survival data.
